### 2011-05-05 paper/paper.tex
Small language change in the introduction and added proof for symmetric transitions

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. We phrase the problem as follows: we are given a convex region $\mathcal{R}$ in the form of a \emph{membership oracle}, a black box which can determine whether any point $x$ is in $\mathcal{R}$, along with a starting point $x_0$ in $\mathcal{R}$. The task is to sample a point from the region with with a distribution as close to uniform as possible.

@@

\begin{theorem} \end{theorem}

>>>>

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. We phrase the problem as follows: we are given a convex region $\mathcal{R}$ in the form of a \emph{membership oracle} which determines whether a given point $x$ is in $\mathcal{R}$, along with a starting point $x_0$ in $\mathcal{R}$. The task is to sample a point from the region with with a distribution as close to uniform as possible.

@@

\begin{theorem}
Any Markov chain whose state space is an open subset of $\mathbb{R}^n$ with a symmetric transition distribution has the uniform distribution as a stationary distribution.
\end{theorem}
\begin{proof}
We will let $S$ be the set of all states of the chain and $P(x,y)$ be the value of the transition distribution associated with moving from $x$ to $y$. Furthermore, let $\mu$ be the uniform distribution on $S$, i.e. $\mu(x) = \frac{1}{\text{Vol}(S)}$. Then we want to show that for every subset $A \subseteq S$, $\int_A (\mu P)(y)\, dy = \frac{\text{Vol}(A)}{\text{Vol}(S)}$. To do this, notice the following:
\begin{align*}
\int_A (\mu P)(y)\, dy &= \int_A \int_S \mu(x)P(x,y)\, dx\, dy \\
&= \int_S \int_A \mu(y)P(y,x)\, dy\, dx
\end{align*}
where here we have used the fact that $\mu(x) = \mu(y)$, $P(x,y) = P(y,x)$, and that we can interchange the order of integration by Fubini's theorem because the double integral is a probability, and therefore finite and the integrand is always positive. However, we can see that this last quantity is the probability of starting at a point in $A$ and moving to a point in $S$. Since we will always move to a point in $S$, that quantity is just the probability that we start in $A$, which is simply $\int_A \mu(y)\, dy = \frac{\text{Vol}(A)}{\text{Vol}(S)}$, as desired.
\end{proof}
